Visually pleasing knot projections

### 2021-09-26 inst/jma_rebuttal.tex

The paper also needs to do a far stronger job of placing itself within
the relevant literature. Simply showing that a single diagram from
wikipedia has weaknesses is not sufficient. The nineteenth century
series of papers ``On Knots" by Peter Guthrie Tait in the Transactions
of the Royal Society of Edinburgh contain far superior images for
example. This is not the first paper to look at making pleasing knot
diagrams, the software knotplot for example offers many tools to do a
similar optimisation to the one discussed here, but is not cited,
Laura Taalman and Colin Abrams among others have multiple papers
addressing the creation of different knot representations and
optimising their form. More broadly the idea of using optimisation in
mathematical art has been used widely, the work of Robert Bosch and
Craig Kaplan springing immediately to mind.

For these reasons the current paper is not really strong enough for
publication. In order to get strong enough I would propose three major
pieces of work:

1) Conduct a thorough literature review of work on the creation of
knot diagrams and their aesthetics and place this paper into that
context as well as the broader context of optimisation in art. % issue~#39

\textcolor{blue}{I have added a literature review as suggested that
  discusses knot diagrams from early Celtic artwork through to
  mathematica.\\ \\ The referee makes the perfectly reasonable
  suggestion of discussing the broader context of optimization of art.
  I will address this comment colloquially.  It is obvious to me, and
  clearly to the referee as well, that numerical optimization
  techniques are well-suited to ``rounding off rough edges'' from a
  wide range of applications; and further that numerical optimization
  will produce ``nice looking'' results.  I have cited some of the
  more prominent workers in the field, whose work is closest to 2D
  knot projections.}

### 2021-09-26 inst/jma_knot.tex
fixes #41

To beautify it we need to specify a function of the path that
quantifies its displeasingness, and then minimize this objective
function using numerical methods.

>>>>

To beautify it we need to specify a function of the path that
quantifies its displeasingness, and then minimize this objective
function using numerical methods.  In the package, minimization is
performed using either Nelder-Mead~\cite{nelder1965} or a Newton-type
method~\cite{dennis1983} (gradient information is not available).  The
optimization typically proceeds over $\mathbb{R}^{50}$ and in the
context of the package, the methods appear to be broadly comparable.
